##=================================================
##Title: "Reproducible Research: Peer Assessment 1"
##Author: "Ulugbek Ruziev"
##Date: "December 20, 2015"
##=================================================
#Reproducible Research: Peer Assessment 1
##Initial settings
```{r}
require("dplyr") ## dplyr is used for structuring the data for analysis
require("ggplot2") ## ggplot2 is required for several plots
require("lattice") ## lattice plot is required for the weekday-weekend plot
echo = TRUE  # Always make code visible
options(scipen = 999)  # Turn off scientific notations for numbers
```
##Loading and preprocessing the data
```{r}
activity <- read.csv(unz("activity.zip","activity.csv")) ## read in the data
activity <- tbl_df(activity) ## structure the data as a tbl class
```
##What is mean total number of steps taken per day?
For this part of the assignment, you can ignore the missing values in the dataset. Make a histogram of the total number of steps taken each day

First I aggregate the number of steps per day. I use the group_by function and then the summarise function from dplyr to perform the aggregation of steps by day and last the hist function to create the histogram plot
```{r}
activity_days <- activity %>% group_by(date) %>% summarise(total.steps = sum(steps))
hist(activity_days$total.steps, breaks = 25, main = "Histogram of Total Steps per Day")
```

Calculate and report the mean total number of steps taken per day
```{r}
mean((activity_days$total.steps), na.rm = TRUE)
```

The mean number of steps taken per day is 10766

Calculate and report the median total number of steps taken per day

```{r}
median((activity_days$total.steps), na.rm = TRUE)
```
The median number of steps taken per day is 10765


